Carbonate chemistry at Ny-Ålesund

### 2022-12-26 awipev-CO2.Rmd
minor corrections

```{r, eval=FALSE, echo=FALSE}
# skipped because it is done in the "stratification tab"
Extreme differences: `r dplyr::filter(tmp, range_diff < -3 | range_diff > 2)`.

There are `r sum(!is.na(tmp$range_diff))` days with salinity values at both 1 m (0-2 m) and 10 m (8-12 m).

The salinity difference between 1 and 10 m ranges between `r min(tmp$range_diff, na.rm = TRUE)` and `r max(tmp$range_diff, na.rm = TRUE)` (mean: `r mean(tmp$range_diff, na.rm = TRUE)`; `r median(tmp$range_diff, na.rm = TRUE)`). The difference with depth is therefore significant.
```

@@

```{r, eval=FALSE, echo=FALSE}
# skipped because it is done in the "stratification tab"
There are `r sum(!is.na(tmp$range))` days with temperature values at
both 1 m (0-2 m) and 9 m (> 8 m). The temperature difference between 1
and 9 m ranges between `r min(tmp$range, na.rm = TRUE)`°C and
`r max(tmp$range, na.rm = TRUE)`°C (mean:
`r mean(tmp$range, na.rm = TRUE)`°C; `r median(tmp$range, na.rm = TRUE)`°C).
The difference with depth is therefore significant.
```

>>>>

```{r, eval=FALSE, echo=FALSE}
# skipped because it is done in the "stratification tab"
# Extreme differences: `r dplyr::filter(tmp, range_diff < -3 | range_diff > 2)`.
# 
# There are `r sum(!is.na(tmp$range_diff))` days with salinity values at both 1 m (0-2 m) and 10 m (8-12 m).
# 
# The salinity difference between 1 and 10 m ranges between `r min(tmp$range_diff, na.rm = TRUE)` and `r max(tmp$range_diff, na.rm = TRUE)` (mean: `r mean(tmp$range_diff, na.rm = TRUE)`; `r median(tmp$range_diff, na.rm = TRUE)`). The difference with depth is therefore significant.
```

@@

```{r, eval=FALSE, echo=FALSE}
# skipped because it is done in the "stratification tab"
# There are `r sum(!is.na(tmp$range))` days with temperature values at
# both 1 m (0-2 m) and 9 m (> 8 m). The temperature difference between 1
# and 9 m ranges between `r min(tmp$range, na.rm = TRUE)`°C and
# `r max(tmp$range, na.rm = TRUE)`°C (mean:
# `r mean(tmp$range, na.rm = TRUE)`°C; `r median(tmp$range, na.rm = TRUE)`°C).
# The difference with depth is therefore significant.
```
